\resizebox{\textwidth}{!}{%
\scriptsize
\begin{forest}
 for tree={draw,align=left,base=top,ignore edge},
 forked edges, remember picture,
 [\textbf{(1) Prototypical-Determinative-Compound-Construction}\\
 \begin{tabular}{p{9cm}@{~}p{9cm}}
  \bfseries Form: & \bfseries Meaning (narrow):\\
  {[[Lexeme][+/-LE][Lexeme]\textsubscript{+/-valent}]}\textsubscript{+/-SynthC} & ``Specification of B through A'': Instantiation of subject-orientated{,} object-orientated{,} attribute-like and averbial patterns.\\
  Gender/Part of Speech: like B & Naming function\\
  \end{tabular},name=proto,delay={tikz={\draw[fill=gray](.210) -- (.330)--(!1.north)--cycle;\node [below=\baselineskip of .345] {Partial inheritance of features};}}
    [\textbf{(2) Phrasal-Compound-Construction}\\
     \begin{tabular}{p{9cm}@{~}p{9cm}}
      \bfseries Form: & \bfseries Meaning (narrow):\\
      {[[Syntagma][+/-LE]\newline [Substantive]\textsubscript{non-derived\slash de-adj.\slash de-subst.\slash deverbal{;} +/-valent}]}\textsubscript{N{;}+/-SynthC} & ``Specification of B through A'': Instantiation of subject-orientated{,} object-orientated{,} attribute-like and averbial patterns.\\
      Gender/Part of Speech: like B{;} +/- word-specific features & Naming function \slash assertion function\\
      \multicolumn{2}{l}{\bfseries Pragmatic:}\\
      \multicolumn{2}{p{18cm}}{Communicative advantages over sentences{;} +/--specific communicative functions{;} more expressive than prototypical determinative compounds}
     \end{tabular}, no edge,l=3cm
      [\textbf{(3.1) Attribute-like-Construction}\\
      {[[Sentence/sentence-like structure\textsubscript{-Proper Name}/Phrase\textsubscript{+CM}]-}\\\relax {[Substantive]\textsubscript{non-derived/de-adj./de-subst./deverb.}]}\textsubscript{N;-SynthC}\\
      \textbf{+ specific communicative functions; highly expressive},calign=first
	      [\textbf{(4.1) Attribute-like-Construction}\\
	      {[[Sentence/sentence-like str.\textsubscript{-Proper Name} / Phrase\textsubscript{+CM}]}\\ - {[Substantive]\textsubscript{non-der./de-adj./de-subst./deverb.; +/-valent}]}
		[\textbf{(5.1) Explikative-Constr.}\\
		{[S-entire/S-ellipt/SScheme-ellipt/}\\
		{VG\textsubscript{+CM}/Phrase\textsubscript{+CM}]}\textsubscript{-Prop.Name}\\
		- {[Substantive]}
		,name=expli]
	      ]
      ]
      [\textbf{(3.2) Attribute-like- / Adverbial- / Subject-orientated- / Object-orientated - Constr.}\\
      {[[Phrase\textsubscript{-CM}/Sentence\textsubscript{+Proper Name}]} - {[Substantive] \textsubscript{non-derived/de-adj./de-subst./deverb.}]}\textsubscript{N;+/-SynthC}\\
      \textbf{- specific communicative functions; slightly expressive}
	  [\textbf{(4.2) Attribute-like-Constr.}\\
	  {[[Phrase\textsubscript{-CM}/Sentence\textsubscript{+Prop.Name}]-}\\
	  {[Substantive]\textsubscript{non-der./de-adj./de-subst./}}\\{\textsubscript{deverb.;+/-valent}]},calign=first	
	    [\textbf{(5.2) Domain-Construction}\\
	     {[Phrase\textsubscript{-KM}/Sentence\textsubscript{+Prop.Name}] -}\\
	     {[Substantive]}
	    ]
	    [\textbf{(5.3) Theme-Construction}\\
	     {[Phrase\textsubscript{-CM}/Inf-koord/VG\textsubscript{-CM}/}\\
	     {Sentence\textsubscript{+Prop.Name}] - [Substantive]}
	    ]
	    [\textbf{(5.4) Qualitative-Construction}\\
	     {[Phrase\slash VG\textsubscript{-CM}] - [Concrete noun]}
	    ]
	    [\textbf{(5.5) Constitutional-Construction}\\
	     {[NP\_\{Num/Adj\}] - [Collective noun]}
	    ]
	  ]
	  [\textbf{(4.3) Adverbial-Constr.}\\
	  {[[Phrase\textsubscript{-CM}/Sentence\textsubscript{+Prop.Name}]-}\\
	  {[Substantive]\textsubscript{de-subst./deverb.;+/-valent}]}	
	  ]
	  [\textbf{(4.4) Subject-orientated-Constr.}\\
	  {[[Phrase\textsubscript{-CM}/Sentence\textsubscript{+Prop.Name}]-}\\
	  {[Substantive]\textsubscript{non-der./de-adj./de-subst./}}\\{\textsubscript{deverb.;+valent/agentiv}]}	
	  ]
	  [\textbf{(4.5) Object-orientated-Constr.}\\
	  {[[Phrase\textsubscript{-CM}/Sentence\textsubscript{+Prop.Name}]-}\\
	  {[Substantive]\textsubscript{de-adj./deverb.;+valent}]}	
	  ]
      ]
    ]
 ,delay={tikz={
 		\path let \p1=($(proto.north west)+(-1cm,0)$), \p2=(expli.south west) in coordinate (newexpli) at (\x1,\y2);
 		\draw (newexpli) -- ($(proto.north west) + (-1cm,0)$) node [midway,above,sloped] {Level of abstractness} node [at start,below] {Low} node [at end,above] {High};
  }}] 
\end{forest}}